### 2014-07-25 Docs/flowchart/flowchart.tex
updated to include delta chi update for volume discrepancy for both full and base state velocity

\subsection{Volume Discrepancy Changes}
\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \overline{p(\rho,h,X_k)^n}$.
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\}.
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \left[\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}\right]/2$.
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left\{\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{\nph,\star}} p_0^{\nph,\star}} \left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\},
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}

>>>>

\subsection{Volume Discrepancy Changes}
\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^n = \overline{p(\rho,h,X_k)^n}$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} = \overline{S^{\nph,\star\star}} - \frac{1}{\overline{\Gamma_1^n}p_0^n}\psi^{\nmh} - \underbrace{\frac{f}{\overline{\Gamma_1^n}p_0^n}\left(\frac{p_0^n-\overline{p_{\rm EOS}^n}}{\Delta t}\right)}_{\delta\chi_{w_0}}.
\end{equation}
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left[ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \underbrace{\frac{f}{\gammabar^n p_0^n}
\left(\frac{p_{\rm EOS}^n - \overline{p_{\rm EOS}^n}}{\Delta t^n}\right)}_{\delta\chi}\right].
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by first defining $p_{\rm EOS}^{n+1,\star} = p(\rho,h,X_k)^{n+1,\star}$,
$\overline{\Gamma_1^{\nph,\star}} = (\overline{\Gamma_1^{n}}+\overline{\Gamma_1^{n+1,\star}})/2$,
and $p^{\nph,\star} = (p^{n}+p^{n+1,\star})/2$, and then using:
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = \overline{S^{\nph,\star}} - \frac{1}{\overline{\Gamma_1^{\nph,\star}}p_0^{\nph,\star}}\psi^{\nph,\star} - \frac{f}{\overline{\Gamma_1^{n+1,\star}}p_0^{n+1,\star}}\left(\frac{p_0^{n+1,\star}-\overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t}\right) - \delta\chi_{w_0}
\end{equation}
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left[\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{n+1,\star}} p_0^{n+1,\star}} \left(\frac{p_{\rm EOS}^{n+1,\star} - \overline{p_{\rm EOS}^{n+1,\star}}}{\Delta t^n}\right) + \delta\chi\right],
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}
